Paper

### 2021-12-14 Paper.Rmd
Tried running bootstrap

Results:
Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected. Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
```{r, cache=TRUE}
plot_dat <- get_bootstrap_cis(days=150, num_subjects=1000, x_dim=1, y_dim=1, I_0=5, inf_dist=0.01, sample_size=20, prop_vac = 0.8)

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')

>>>>

Results:
Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected. Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
```{r, cache=TRUE}
plot_dat <- get_bootstrap_cis(days=100, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.1, sample_size=20, prop_vac = 0.8)

ggplot() +
  geom_line(aes(x=1:101, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:101, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:101, y=plot_dat[ ,3]), linetype = 2, color = 'red')
